Signal Processing to Demodulate FM Radio

### 2020-12-13 doc/paper/paper.tex
update

  \subsubsection{FM Channel Allocation}
    %https://www.electronics-notes.com/articles/audio-video/broadcast-audio/vhf-fm-frequency-modulation-basics.php
    The entire FM band frequency range divides into multiple channels which can be used.
    In Europe, the European Telecommunications Standards Institute (ETSI) sets the respective standards for the usage of these frequencies.
    The main specifications for a single FM broadcasting channels are explained in this section.
    Each channel may allocate a bandwidth of 200 kHz.
    Within a channel, the maximum deviation from the center frequency shall not exceed 75 kHz.
    This leaves a guard band of 25 kHz on either side, to minimize interference with adjacent channels.
    Center frequencies may be allocated on multiples of 100 kHz.
    A sum of the left and right audio channel is located starting from 30 Hz, up to 15 kHz.
    The lower limit at 30 Hz is to prevent the transmission of a direct current (DC) part, which would require a large amount of power in transmission. This effect is one of the downsides of amplitude modulation (AM), where the carrier is located at the channels' center frequeny and requires a high transmission power. % TODO: check this fact
    The upper limit at 15 kHz is chosen, to maintain a sufficient spacing to the first subcarrier.
    This subcarrier is allocated at an offset of 19 kHz from the carrier.
    It is also called the 'pilot tone', since it is a continuous signal.
    The pilot tone is used to synchronize the left and right channel of an audio signal, to generate stereo audio.
    The center frequency for stereo audio is located at 38 kHz, which is an integer multiple of 19 kHz for practical reasons.
    A signal that is constructed of the difference between left and right audio channel is modulated on the 38 kHz subcarrier.
    The bandwidth for the difference-signal spans 15 kHz on either side.

    \begin{figure}[!h]
      \centering
        \includegraphics[width=7cm]{img/fm-channel-baseband.png}
      \caption{Allocation of frequencies in an FM channel}
      \label{fig_sim}
    \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FM Signal Demodulation}

  \subsection{Baseband Delay Demodulator}
  \subsection{Phase-Adapter Demodulator}
  \subsection{Phase-Locked Loop (PLL)}
  \subsection{Mixed Demodulator}

>>>>

  \subsection{Channel Frequency Spectrum}
    %https://www.electronics-notes.com/articles/audio-video/broadcast-audio/vhf-fm-frequency-modulation-basics.php
    The entire FM band frequency range divides into multiple channels which can be used.
    In Europe, the European Telecommunications Standards Institute (ETSI) sets the respective standards for the usage of these frequencies.
    The main specifications for a single FM broadcasting channels are explained in this section.
    Each channel may allocate a bandwidth of 200 kHz.
    Within a channel, the maximum deviation from the center frequency shall not exceed 75 kHz.
    This leaves a guard band of 25 kHz on either side, to minimize interference with adjacent channels.
    Center frequencies may be allocated on multiples of 100 kHz.
    \ref{sec_fm_sig_demod} shows the upper half-bands' frequency spectrum of a single channel.
    A sum of the left and right audio channel is located starting from 30 Hz, up to 15 kHz.
    The summation of left and right audio channel resembles the mono audio stream.
    The lower limit at 30 Hz is to prevent the transmission of a direct current (DC) part, which would require a large amount of power in transmission. This effect is one of the downsides of amplitude modulation (AM), where the carrier is located at the channels' center frequeny and requires a high transmission power. % TODO: check this fact
    The upper limit at 15 kHz is chosen, to maintain a sufficient spacing to the first subcarrier.
    This subcarrier is allocated at an offset of 19 kHz from the carrier.
    It is also called the 'pilot tone', since it is a continuous signal.
    The pilot tone is used to synchronize the left and right channel of an audio signal, to generate stereo audio.
    The center frequency for stereo audio is located at 38 kHz, which is an integer multiple of 19 kHz for practical reasons.
    However, the 38 kHz carrier is suppressed and thus not visible in the received spectrum.
    It can still be recovered, since it is phase coherent with the 19 kHz pilot tone per definition.
    A signal that is constructed by the difference between left and right audio channel is modulated on a 38 kHz subcarrier.
    The bandwidth for this difference-signal spans 15 kHz on either side of the subcarrier.
    This signal is used to generate a stereo audio signal, in combination with the mono signal.
    This process is explained into more detail in chapter \ref{sec_fm_sig_demod}.
    Considering all these parts in the spectrum, there is still bandwidth free to use, up to the maximum channel bandwitdh 100 kHz in one sideband.
    Because of that, additional services were added to the audio transmission, to provide additional data services and information.
    Services that were implemented are the Data Radio Channel (DARC), which is mostly used in Japan and the USA, the Subsidary Communication Authorization (SCA) and the Radio Data System (RDS).
    Out of these, RDS is the most significant service in Europe.
    It is used to transmit additional information about the channel, such as the radio stations' name, currently playing songs' title or traffic information.

    \begin{figure}[!h]
      \centering
        \includegraphics[width=7cm]{img/fm-channel-baseband.png}
      \caption{Allocation of frequencies in an FM channel}
      \label{fig_channel_baseband_freqs}
    \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FM Signal Demodulation}
\label{sec_fm_sig_demod}
    % mono:   just LP on 15 kHz
    % stereo: sum (L+R) + (L-R) = 2 L, (L+R) - (L-R) = 2R
  \subsection{Baseband Delay Demodulator}
  \subsection{Phase-Adapter Demodulator}
  \subsection{Phase-Locked Loop (PLL)}
  \subsection{Mixed Demodulator}
